Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-10 article.tex
remove todo

Finally since there is a high correlation between neurons, we made a
low-rank hypothesis and perform noise filtering through a principal component
approach [TODO cite]. From the $p$ eigen vectors, we only kept $80\%$ of
the eigen vectors which have the largest eigen value. In the context of the
challenge, this assumption was verified on all provided dataset

>>>>

Finally since there is a high correlation between neurons, we made a
low-rank hypothesis and perform noise filtering through a principal component
approach. From the $p$ eigen vectors, we only kept $80\%$ of
the eigen vectors which have the largest eigen value. In the context of the
challenge, this assumption was verified on all provided dataset
